Template Master's Thesis

### 2023-08-18 paper.tex
Update discussion

Address clustering through node embedding methods proved to be the most effective approach in our analysis. Unlike methods that require participation in specific on-chain events, node embedding examines the entire interaction network between addresses, making it broadly applicable. Our implementation of node embedding methods differs from previous approaches by \cite{Beres2020} and \cite{wu2022tutela}. We construct the network graph based on asset transfers between addresses of our predefined set and analyze on-chain data from two distinct blockchain networks: Polygon and Ethereum. \newline
The main reasons for this are the different clustering objectives of previous implementations. \cite{wu2022tutela} aimed to cluster addresses without a predefined set, therefore using transaction data for network graph construction. Conversely, \cite{Beres2020} try to match deposit and withdrawal addresses for Tornado Cash, relying on all token transfers and transactions to cluster addresses based on similar on-chain behavior. Since it is not likely that withdrawal and deposit addresses from Tornado cash interacted with each other, the approach chosen by \cite{Beres2020} is better suited for that specific case.\newline
We validated our approach using ENS address pairs as ground truth and found better results in terms of average rank, when building the network graph out of intra-set asset transfers compared to using all token transfer events or transactions. \newline
Subsequently, we applied three node embedding algorithms that showed strong performance in the experiments of \cite{Beres2020} and compared their effectiveness. Our results indicate that Role2Vec is the best-performing method, locating the ground truth pair within the five nearest neighbors in 70\% of cases. This contrasts with previous findings, which identified Diff2Vec as the most effective method. \newline
Determining why one approach outperforms another is challenging. Both Diff2Vec and DeepWalk preserve neighborhood characteristics, while Role2Vec is a structural node embedding method, meaning that ... A possible explanation is that Role2Vec ... % expand on structural node embedding and give possible explanation
Nevertheless, given the small sample size and the overall strong performance of all methods, the differences in results might be specific to the data at hand. \newline
We devised a novel method for creating clusters from our node embeddings, enabling us to estimate the number of entities represented by the 51,566 network graph nodes/addresses. This method involved calculating the Euclidean distance between pairs of feature vectors, specifically using the node embedding matrix generated by Role2Vec. Nodes were clustered if their distance fell below a predetermined threshold, and any overlapping clusters were subsequently merged. \newline
Though our method may not be the ideal approach for clustering, it is likely more effective than simply clustering a fixed number of $k$ addresses. We observed that the number of clusters and their size is highly sensitive to the chosen distance threshold, making it challenging to assess the accuracy of these clusters. We have provided a sensitivity analysis to illustrate this issue. The distances between the feature vectors tend to be quite narrow (dense vectors), and even the distances between ground truth pairs exhibit significant variation. \newline
We explored potential enhancements to our method, such as incorporating additional information (e.g., Time of Day, normalized Gas) into the feature vectors. Unfortunately, these modifications did not yield improvements. Similarly, a two-step approach to clustering also proved unsuccessful. These areas remain open for future research.

>>>>

Address clustering through node embedding methods proved to be the most effective approach in our analysis. Unlike methods that require participation in specific on-chain events, node embedding examines the entire interaction network between addresses, making it broadly applicable. \newline
Our implementation of node embedding methods differs from previous approaches by \cite{Beres2020} and \cite{wu2022tutela}. We construct the network graph based on asset transfers between addresses of our predefined set and simultaneously analyze data from Polygon and Ethereum. The main reason is previous implementations' different settings and research questions. \cite{wu2022tutela} aim to cluster addresses without a predefined set, therefore using transaction data for network graph construction. Conversely, \cite{Beres2020} try to match deposit and withdrawal addresses for Tornado Cash, relying on all token transfers and transactions to cluster addresses based on similar on-chain behavior. Since it is not very common that Tornado cash withdrawal and deposit addresses interact with each other, the approach chosen by \cite{Beres2020} is better suited for their objectives. \newline
We validated our approach using ENS address pairs as ground truth and found better results in terms of average rank, when building the network graph out of intra-set asset transfers compared to using all token transfer events or transactions. \newline
Subsequently, we applied three node embedding algorithms that showed strong performance in the experiments of \cite{Beres2020} and compared their effectiveness. Our results indicate that Role2Vec is the best-performing method, locating the ground truth pair within the five nearest neighbors in 70\% of cases. This contrasts with previous findings, which identified Diff2Vec as the most effective method out of the three. \newline
Determining why one approach outperforms another is challenging. Both Diff2Vec and DeepWalk preserve neighborhood characteristics, while Role2Vec is a structural node embedding method, meaning that ... A possible explanation is that Role2Vec ... % expand on structural node embedding and give possible explanation
Nevertheless, given the small sample size, possible flaws in the evaluation via average rank and the overall strong performance of all methods, the differences in results might be specific to the data at hand. \newline
Next, we created clusters from our node embeddings, enabling us to estimate the number of entities represented by the 51,566 network graph nodes representing addresses. Our method involves calculating the Euclidean distance between pairs of feature vectors, specifically using the node embedding matrix generated by Role2Vec. Nodes are clustered if their distance falls below a predetermined threshold, and any overlapping clusters are subsequently merged. \newline
Though our method may not be the ideal approach for clustering, it is likely more effective than simply clustering a fixed number of $k$ addresses. We observed that the number of clusters and their size is highly sensitive to the chosen distance threshold, making it challenging to assess the accuracy of these clusters. We have provided a sensitivity analysis to illustrate this issue. The distances between the feature vectors tend to be quite narrow (dense vectors), and even the distances between various ground truth pairs exhibit significant variation. \newline
We explored potential enhancements to our method, such as incorporating additional information, e.g., time-of-day-activity and/or gas price selection into the feature vectors. Unfortunately, these modifications did not yield improvements. Similarly, a two-step approach to clustering also proved unsuccessful. These areas remain open for future research.
